A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-03-01 sections/conclusion.tex
more on conclusion

Outline:
\begin{itemize}
    \item difficulties following DK's formalization
    \item a blend of ideas from various sources DK's ordered contexts
    \item list of judgements + some novel ideas
    \item lessons learned: problems identified in proofs and scoping
    \item Future work
\end{itemize}

>>>>

Outline:
\begin{itemize}
    \item difficulties following DK's formalization
    \item a blend of ideas from various, including sources DK's ordered contexts
    \item list of judgements + some novel ideas
    \item lessons learned: problems identified in proofs and scoping
    \item Future work
\end{itemize}

Our judgment form, the worklist, is shown to be an elegant way to
formalize higher-order type infernce algorithms.
By mixing judgment chains with variable declarations in a single sort,
variable scopings are easily controlled by the ordered context in a natural way.

The formal proof in Abella convinces us of the correctness of our algorithm,
which further indicates that DK's algorithm, sharing a similar solving procedure as ours,
should be a correct one.
